Generalising Weighted Model Counting to Boolean Algebras

### 2020-04-09 paper.tex
More feedback

\title{On the Limitations of Weighted Model Counting}
%\title{Weighted Model Counting/Integration from the Perspective of Boolean Algebras}
%\title{What Boolean Algebras Can Teach Us About Weighted Model Counting/Integration?}
\author{Paulius Dilkas}

@@

% Contributions:
% 1. A generalisation of WMC adapted to Boolean algebras.
% 2. We show that it is a valid measure.
% 3. We show that WMC assumes independence, i.e., cannot represent all measures.
% 4. We show how the BA can be extended with new 'literals' to represent any measure.
% 5. (Maybe) we establish a lower bound on the number of new literals, if we
% make no assumptions about independence.
% 6. show how evidence = quotiening by a filter, and how quotiening by an ideal works
% 7. (WMI) If all weights are 1, we extend Boolean variables to discrete
% variables, and continuous variables are arbitrary subsets (in the
% sigma-algebra), then the WMI process calculates the probability of any event
% and doesn't require going down to the level of models (assuming a suitable
% probability measure).
% 8. If the weight of a literal (and its negation) is 1, then we don't need to
% look at its models--the probability can be calculated at any level. This
% extends to any number of variables.
% 9. How WMI transforms to our algebras. The boring version and what's wrong
% with it.
% 10. Show how to transfer the measure to a quotient algebra and that the answer
% match with each other and with the original definition of WMC.

Previous/related work:
\begin{itemize}
\item Hailperin's approach to probability logic
  \cite{DBLP:journals/ndjfl/Hailperin84}
\item Nilsson's (somewhat successful) probabilistic logic
  \cite{DBLP:journals/ai/Nilsson86}
\item Logical induction: a huge paper with a good overview of previous attempts
  to assign probabilities to logical sentences in a way that makes sense
  \cite{DBLP:journals/eccc/GarrabrantBCST16}.
\item Semiring programming \cite{DBLP:journals/corr/BelleR16}
\item WMI \cite{DBLP:conf/ijcai/BellePB15}
\item Measures on Boolean algebras: more specific articles
  \begin{itemize}
  \item On possibility and probability measures in finite Boolean algebras
    \cite{DBLP:journals/soco/CastineiraCT02}
  \item Representation of conditional probability measures
    \cite{krauss1968representation}
  \end{itemize}
\end{itemize}

@@

@@

\begin{lemma}[\cite{horn1948measures}] \label{lemma:m_and_order}
  Let $m: \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure. For any $a, b \in
  \mathbf{B}$, if $a \le b$, then $m(a) \le m(b)$.
\end{lemma}

@@

@@

@@

\begin{definition} \label{def:wmc}
  Let $\mathbf{B}$ be an atomic BA, and let $M \subset \mathbf{B}$ be its set of
  atoms. Let $L \subset \mathbf{B}$ be such that every atom $m \in M$ can be
  uniquely expressed as $m = \bigwedge L'$ for some $L' \subseteq L$, and let
  $w\colon L \to \mathbb{R}_{\ge 0}$ be arbitrary. The \emph{weighted model
    count} $\WMC_w\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ is defined as
  \[
    \WMC_w(x) = \begin{cases}
      0 & \text{if } x = 0 \\
      \prod_{l \in L'} w(l) & \text{if } M \ni x = \bigwedge L' \\
      \sum_{\text{atoms } a \le x} \WMC_w(a) & \text{otherwise}
    \end{cases}
  \]
  for any $x \in \mathbf{B}$. Furthermore, we define the \emph{normalised
    weighted model count} $\nWMC_w\colon \mathbf{B} \to [0, 1]$ as $\nWMC_w(x) =
  \frac{\WMC_w(x)}{\WMC_w(1)}$ for all $x \in \mathbf{B}$. For both $\WMC_w$ and
  $\nWMC_w$, we will drop the subscript when doing so results in no potential
  confusion.
%  Finally, we say that a measure $m\colon \mathbf{B} \to
%  \mathbb{R}_{\ge 0}$ is a \emph{WMC measure} (or is \emph{WMC-computable}) if
%  there exists a subset $L \subset \mathbf{B}$ and a weight function $w\colon L
%  \to \mathbb{R}_{\ge 0}$ such that $m = \WMC_w$.
\end{definition}
% TODO: mention that the definition can be reduced to a single formula (i.e.,
% without cases)
% TODO: any measure is a WMC measure if all atoms are in L

\begin{proposition}
  $\WMC$ is a measure, and $\nWMC$ is a probability measure.
\end{proposition}
\begin{proof}
  First, note that $\WMC$ is non-negative and $\WMC(0) = 0$ by definition. Next,
  let $x, y \in \mathbf{B}$ be such that $x \land y = 0$. We want to show that
  \begin{equation} \label{eq:additivity_proof}
    \WMC(x \lor y) = \WMC(x) + \WMC(y).
  \end{equation}
  If, say, $x = 0$, then \cref{eq:additivity_proof} becomes
  \[
    \WMC(y) = \WMC(0) + \WMC(y) = \WMC(y)
  \]
  (and likewise for $y = 0$). Thus we can assume that $x \ne 0 \ne y$ and use
  \cref{thm:representation} to write
  \[
    x = \bigvee_{i \in I} x_i \quad \text{and} \quad y = \bigvee_{j \in J} y_j
  \]
  for some sequences of atoms $(x_i)_{i \in I}$ and $(y_j)_{j \in J}$. If
  $x_{i'} = y_{j'}$ for some $i' \in I$ and $j' \in J$, then
  \[
    x \land y = \bigvee_{i \in I} \bigvee_{j \in J} x_i \land y_j = x_{i'} \land
    y_{j'} \ne 0,
  \]
  contradicting the assumption. This is enough to show that
  \begin{align*}
    \WMC(x \lor y) &= \WMC\left( \left( \bigvee_{i \in I} x_i \right) \lor \left(\bigvee_{j \in J} y_j \right) \right) = \sum_{i \in I} \WMC(x_i) + \sum_{j \in J} \WMC(y_j) \\
                   &= \WMC(x) + \WMC(y),
  \end{align*}
  finishing the proof that $\WMC$ is a measure. This immediately shows that
  $\nWMC$ is a probability measure since, by definition, $\nWMC(1) = 1$.
\end{proof}

@@

@@

\begin{proposition}[Measures on quotients] \label{def:measures_on_quotients}
  Let $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure, and let $(p)$ be
  a principal ideal. Let $m^*\colon \mathbf{B}/(p) \to \mathbb{R}_{\ge 0}$ be
  defined as
  \[
    m^*(a/(p)) = m(a \lor p)
  \]
  for any $a \in \mathbf{B}$. The function $m^*$ is well-defined. Furthermore,
  it is a measure on $\mathbf{B}/(p)$ if and only if $m(p) = 0$. Moreover, if it
  is a measure, then the following properties transfer from $m$ to $m^*$:
  \begin{itemize}
  \item if $m$ is a \emph{probability measure}, then so is $m^*$;
  \item if $m$ is \emph{strictly positive}, then so is $m^*$.
  \end{itemize}
\end{proposition}
\begin{proof}
  \Cref{lemma:well-defined} proves that the function is well-defined. Next,
  note that
  \[
    m^*(0/(p)) = m(0 \lor p) = m(p),
  \]
  so $m^*(0/(p)) = 0$ if and only if $m(p) = 0$. For the second part of
  \cref{def:measure}, let $a/(p), b/(p) \in \mathbf{B}/(p)$ be such that
  \[
    a/(p) \land b/(p) = a \land b / (p) = 0 / (p).
  \]
  This condition is equivalent to $a \land b \in (p)$ and $(a \land b) \lor p =
  p$ by well-known properties of quotients and ideals
  \cite{givant2008introduction}, \cref{def:ideal}, and the definition of $\le$,
  respectively. Now
  \begin{align*}
    m^*(a/(p) \lor b/(p)) &= m^*(a \lor b / (p)) = m(a \lor b \lor p) = m((a \lor p) \lor (b \lor p)) \\
                          &= m(a \lor p) + m(b \lor p) - m((a \lor p) \land (b \lor p)) \\
                          &= m^*(a/(p)) + m^*(b/(p)) - m((a \lor p) \land (b \lor p))
  \end{align*}
  by \cref{lemma:sum}. However
  \[
    (a \lor p) \land (b \lor p) = (a \land b) \lor p = p,
  \]
  so $m^*(a/(p) \lor b/(p)) = m^*(a/(p)) + m^*(b/(p))$ if and only if $m(p) = 0$.

  The two remaining properties are easy to prove:
  \begin{itemize}
  \item If $m(1) = 1$, then $m^*(1/(p)) = m(1 \lor p) = m (1) = 1$.
  \item Suppose that $m$ is strictly positive, and let $a/(p) \in
    \mathbf{B}/(p)$ be such that $a/(p) \ne 0/(p)$. Then
    \[
      m^*(a/(p)) = m(a \lor p) \ge m(a) > 0,
    \]
    where the first inequality comes from an elementary property of $\le$ that
    $x \le x \lor y$ for any $x, y \in \mathbf{B}$ \cite{sikorski1969boolean}
    and \cref{lemma:m_and_order}; and the second inequality follows because
    $a/(p) \ne 0/(p)$ implies that $a \ne 0$, and $m$ is assumed to be strictly
    positive.
  \end{itemize}
\end{proof}
% TODO: add parentheses around quotients (e.g., (a+b)/I).
% TODO: I think I need to cite something for: a/I = 0/I <=> a \in I

@@

@@

\begin{proposition}
  Let $\mathbf{B}$ be a finite measure algebra with measure $m\colon \mathbf{B} \to
  \mathbb{R}_{\ge 0}$. Let $L \subset \mathbf{B}$ be defined as
  \[
  L = \{ l_i \mid i \in [n] \} \cup \{ \neg l_i \mid i \in [n] \}
  \]
  for some $n \in \mathbb{N}$. Finally, assume that $\mathbf{B}$ has $2^n$
  atoms, where each atom $a \in \mathbf{B}$ is an infimum
  \[
    a = \bigwedge_{i=1}^n a_i
  \]
  such that $a_i \in \{ l_i, \neg l_i \}$ for $i \in [n]$. Then there exists a
  weight function $w\colon L \to \mathbb{R}_{\ge 0}$ that makes $m$ a WMC measure if
  and only if
  \begin{equation} \label{eq:wmccondition}
  m(l \land l') = m(l)m(l')
  \end{equation}
  for all distinct $l, l' \in L$ such that $l \ne \neg l'$.
\end{proposition}

@@

  Now recall that $m = \nWMC$ and note that \cref{eq:to_prove2} can be
  multiplied by $\WMC(1)^2$ to turn the equation into one for $\WMC$ instead of
  $\nWMC$. Then
  \begin{align*}
    \WMC(k_i \land k_j) &= \sum_{\text{atoms } a \le k_i \land k_j} \WMC(a) = \sum_{\text{atoms } a \le k_i \land k_j} \prod_{m \in [n]} w(a_m) \\
                        &= \sum_{\text{atoms } a \le k_i \land k_j} w(a_i)w(a_j) \prod_{m \in [n] \setminus \{ i, j \}} w(a_m) = \sum_{\text{atoms } a \le k_i \land k_j} w(k_i)w(k_j) \prod_{m \in [n] \setminus \{ i, j \}} w(a_m) \\
    &= w(k_i)w(k_j) \sum_{\text{atoms } a \le k_i \land k_j} \prod_{m \in [n] \setminus \{ i, j \}} w(a_m) = w(k_i)w(k_j)C,
  \end{align*}
  where $C$ denotes the part of $\WMC(k_i \land k_j)$ that will be the same for
  $\WMC(\neg k_i \land k_j)$, $\WMC(k_i \land \neg k_j)$, and $\WMC(\neg k_i
  \land \neg k_j)$ as well. But then \cref{eq:to_prove2} becomes
  \[
    w(k_i)w(k_j)w(\neg k_i)w(\neg k_j)C^2 = w(k_i)w(\neg k_j)w(\neg k_i)w(k_j)C^2
  \]
  which is trivially true. By showing that WMC satisfies \cref{eq:to_prove2}, we
  also showed that it satisfies \cref{eq:to_prove}, finishing the second part of
  the proof.
\end{proof}
% TODO: the auxiliary result should be a 'claim' in-between the theorem and the proof.

@@

@@

% TODO: a section on WMI: 3 results

>>>>

\title{Generalising Weighted Model Counting to Boolean Algebras}
%\title{On the Limitations of Weighted Model Counting}
%\title{Weighted Model Counting/Integration from the Perspective of Boolean Algebras}
%\title{What Boolean Algebras Can Teach Us About Weighted Model Counting/Integration?}
\author{Paulius Dilkas}

@@

% Feedback 2: WMC-Computable -> WMC-Definable

% Feedback 2: The paper at this stage is very technical - the danger is that
% WMC/SRL people may not be able to follow it and so would be hard to get
% accepted. Without clear target audience, [???] get work accepted. My main high
% level suggestion is that let us tease apart what you have and see if a story
% emerges. That is, let us attempt to write a paper *with examples* and see
% whether with significant motivation, we have a story emerging. Below, sample
% text needed to adequately motivate [???] for WMC/SRL community.

% Contributions:
% 1. A generalisation of WMC to Boolean algebras. We show how WMC makes
% independence assumptions and how we can make some but not all literals
% independent.
% 1.5. We show how the lifted inference techniques stem from the underlying
% algebraic structure.
% 1.6. Do we add more inference rules?
% 2. We show that it is a valid measure.
% 3. We show that WMC assumes independence, i.e., cannot represent all measures.
% 4. We show how the BA can be extended with new 'literals' to represent any measure.
% 5. (Maybe) we establish a lower bound on the number of new literals, if we
% make no assumptions about independence.
% 6. show how evidence = quotiening by a filter, and how quotiening by an ideal works
% 7. (WMI) If all weights are 1, we extend Boolean variables to discrete
% variables, and continuous variables are arbitrary subsets (in the
% sigma-algebra), then the WMI process calculates the probability of any event
% and doesn't require going down to the level of models (assuming a suitable
% probability measure).
% 8. If the weight of a literal (and its negation) is 1, then we don't need to
% look at its models--the probability can be calculated at any level. This
% extends to any number of variables.
% 9. How WMI transforms to our algebras. The boring version and what's wrong
% with it.
% 10. Show how to transfer the measure to a quotient algebra and that the answer
% match with each other and with the original definition of WMC.

Potential directions to explore (no good ones, really):
\begin{itemize}
\item Infinite BAs.
  % TODO: Feedback 2: understanding this is the key for formulating the
  % relevance/significance of this work
  \begin{itemize}
  \item For example, the BA of finite and cofinite sets could be interesting.
  \item OUWMC requires infinite logics to be compact (whatever that means). My
    algebraic angle suggests that completeness should be enough. Topologically,
    compactness implies completeness, but I have no idea how this translates to
    logics and algebras.
  \end{itemize}
\item WMI
\item Measures with something other than $\mathbb{R}_{\ge 0}$ as the codomain
  (doesn't look promising).
\end{itemize}

Previous/related work:
\begin{itemize}
\item Hailperin's approach to probability logic
  \cite{DBLP:journals/ndjfl/Hailperin84}
\item Nilsson's (somewhat successful) probabilistic logic
  \cite{DBLP:journals/ai/Nilsson86}
\item Logical induction: a big paper with a good overview of previous attempts
  to assign probabilities to logical sentences in a sensible way
  \cite{DBLP:journals/eccc/GarrabrantBCST16}
\item Semiring programming \cite{DBLP:journals/corr/BelleR16}
\item WMI \cite{DBLP:conf/ijcai/BellePB15}
\item Measures on Boolean algebras
  \begin{itemize}
  \item On possibility and probability measures in finite Boolean algebras
    \cite{DBLP:journals/soco/CastineiraCT02}
  \item Representation of conditional probability measures
    \cite{krauss1968representation}
  \end{itemize}
\end{itemize}

@@

% TODO: Feedback 2: Explain with examples: models = elements [atoms] of algebra

@@

@@

% TODO: Feedback 2: I did a high level read to get the big picture but found
% this discussion on ideals distracting. Specifically, w.r.t. the main claims
% when do these things get used?

@@

% TODO: Feedback 2: Result #1: What are the conditions under which WMC defines a
% measure as introduced above? [Non-negativity should be enough so this is not a
% result.]

@@

% TODO: Feedback 2: You need to explain what precisely these mean in logic and
% models and weight functions are usually defined and understood.
\todo[inline]{This should be replaced with inner sums (a.k.a. free products)}
\begin{definition} \label{def:wmc}
  Let $\mathbf{B}$ be an atomic BA, and let $M \subset \mathbf{B}$ be its set of
  atoms. Let $L \subset \mathbf{B}$ be such that every atom $m \in M$ can be
  uniquely expressed as $m = \bigwedge L'$ for some $L' \subseteq L$, and let
  $w\colon L \to \mathbb{R}_{\ge 0}$ be arbitrary. The \emph{weighted model
    count} $\WMC_w\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ is defined as
  \[
    \WMC_w(x) = \begin{cases}
      0 & \text{if } x = 0 \\
      \prod_{l \in L'} w(l) & \text{if } M \ni x = \bigwedge L' \\
      \sum_{\text{atoms } a \le x} \WMC_w(a) & \text{otherwise}
    \end{cases}
  \]
  for any $x \in \mathbf{B}$. Furthermore, we define the \emph{normalised
    weighted model count} $\nWMC_w\colon \mathbf{B} \to [0, 1]$ as $\nWMC_w(x) =
  \frac{\WMC_w(x)}{\WMC_w(1)}$ for all $x \in \mathbf{B}$. For both $\WMC_w$ and
  $\nWMC_w$, we will drop the subscript when doing so results in no potential
  confusion.
%  Finally, we say that a measure $m\colon \mathbf{B} \to
%  \mathbb{R}_{\ge 0}$ is a \emph{WMC measure} (or is \emph{WMC-computable}) if
%  there exists a subset $L \subset \mathbf{B}$ and a weight function $w\colon L
%  \to \mathbb{R}_{\ge 0}$ such that $m = \WMC_w$.
\end{definition}
% TODO: mention that the definition can be reduced to a single formula (i.e.,
% without cases)
% TODO: any measure is a WMC measure if all atoms are in L

\begin{theorem}
  $\WMC$ is a measure, and $\nWMC$ is a probability measure.
\end{theorem}
% TODO: Feedback 2: Need to explain how WMC and NWMC connects to standard
% definitions of WMC and Pr(phi|e) = WMC(phi /\ e)/WMC(e).
\begin{proof}
  First, note that $\WMC$ is non-negative and $\WMC(0) = 0$ by definition. Next,
  let $x, y \in \mathbf{B}$ be such that $x \land y = 0$. We want to show that
  \begin{equation} \label{eq:additivity_proof}
    \WMC(x \lor y) = \WMC(x) + \WMC(y).
  \end{equation}
  If, say, $x = 0$, then \cref{eq:additivity_proof} becomes
  \[
    \WMC(y) = \WMC(0) + \WMC(y) = \WMC(y)
  \]
  (and likewise for $y = 0$). Thus we can assume that $x \ne 0 \ne y$ and use
  \cref{thm:representation} to write
  \[
    x = \bigvee_{i \in I} x_i \quad \text{and} \quad y = \bigvee_{j \in J} y_j
  \]
  for some sequences of atoms $(x_i)_{i \in I}$ and $(y_j)_{j \in J}$. If
  $x_{i'} = y_{j'}$ for some $i' \in I$ and $j' \in J$, then
  \[
    x \land y = \bigvee_{i \in I} \bigvee_{j \in J} x_i \land y_j = x_{i'} \land
    y_{j'} \ne 0,
  \]
  contradicting the assumption. This is enough to show that
  \begin{align*}
    \WMC(x \lor y) &= \WMC\left( \left( \bigvee_{i \in I} x_i \right) \lor \left(\bigvee_{j \in J} y_j \right) \right) = \sum_{i \in I} \WMC(x_i) + \sum_{j \in J} \WMC(y_j) \\
                   &= \WMC(x) + \WMC(y),
  \end{align*}
  finishing the proof that $\WMC$ is a measure. This immediately shows that
  $\nWMC$ is a probability measure since, by definition, $\nWMC(1) = 1$.
\end{proof}

@@

% TODO: Feedback 2: I look the significance of the below results. Proving
% properties that don't [???] the "roadmap" means (AI) readers will lose
% interest. [This applies until the beginning of the next section.]

@@

% TODO: Feedback 2: Where is this helping?
\todo[inline]{Outdated. $m(a \land \neg p)$ is better than $m (a \lor p)$.}
\begin{proposition}[Measures on quotients] \label{def:measures_on_quotients}
  Let $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure, and let $(p)$ be
  a principal ideal. Let $m^*\colon \mathbf{B}/(p) \to \mathbb{R}_{\ge 0}$ be
  defined as
  \[
    m^*(a/(p)) = m(a \lor p)
  \]
  for any $a \in \mathbf{B}$. The function $m^*$ is well-defined. Furthermore,
  it is a measure on $\mathbf{B}/(p)$ if and only if $m(p) = 0$. Moreover, if it
  is a measure, then the following properties transfer from $m$ to $m^*$:
  \begin{itemize}
  \item if $m$ is a \emph{probability measure}, then so is $m^*$;
  \item if $m$ is \emph{strictly positive}, then so is $m^*$.
  \end{itemize}
\end{proposition}
\begin{proof}
  \Cref{lemma:well-defined} proves that the function is well-defined. Next,
  note that
  \[
    m^*(0/(p)) = m(0 \lor p) = m(p),
  \]
  so $m^*(0/(p)) = 0$ if and only if $m(p) = 0$. For the second part of
  \cref{def:measure}, let $a/(p), b/(p) \in \mathbf{B}/(p)$ be such that
  \[
    a/(p) \land b/(p) = a \land b / (p) = 0 / (p).
  \]
  This condition is equivalent to $a \land b \in (p)$ and $(a \land b) \lor p =
  p$ by well-known properties of quotients and ideals
  \cite{givant2008introduction}, \cref{def:ideal}, and the definition of $\le$,
  respectively. Now
  \begin{align*}
    m^*(a/(p) \lor b/(p)) &= m^*(a \lor b / (p)) = m(a \lor b \lor p) = m((a \lor p) \lor (b \lor p)) \\
                          &= m(a \lor p) + m(b \lor p) - m((a \lor p) \land (b \lor p)) \\
                          &= m^*(a/(p)) + m^*(b/(p)) - m((a \lor p) \land (b \lor p))
  \end{align*}
  by \cref{lemma:sum}. However
  \[
    (a \lor p) \land (b \lor p) = (a \land b) \lor p = p,
  \]
  so $m^*(a/(p) \lor b/(p)) = m^*(a/(p)) + m^*(b/(p))$ if and only if $m(p) = 0$.

  The two remaining properties are easy to prove:
  \begin{itemize}
  \item If $m(1) = 1$, then $m^*(1/(p)) = m(1 \lor p) = m (1) = 1$.
  \item Suppose that $m$ is strictly positive, and let $a/(p) \in
    \mathbf{B}/(p)$ be such that $a/(p) \ne 0/(p)$. Then
    \[
      m^*(a/(p)) = m(a \lor p) \ge m(a) > 0,
    \]
    where the first inequality comes from an elementary property of $\le$ that
    $x \le x \lor y$ for any $x, y \in \mathbf{B}$ \cite{sikorski1969boolean}
    and \cref{lemma:measure_and_order}; and the second inequality follows
    because $a/(p) \ne 0/(p)$ implies that $a \ne 0$, and $m$ is assumed to be
    strictly positive.
  \end{itemize}
\end{proof}
% TODO: add parentheses around quotients (e.g., (a+b)/I).
% TODO: I think I need to cite something for: a/I = 0/I <=> a \in I

@@

\todo[inline]{Proofs need to be updated and propositions could be phrased in a
  better way, but the gist should be the same.}

% TODO: Feedback 2: Result #2: WMC c measures. That is, WMC wight weights on
% literals is less expressive than (a) WMC with weights on models is less
% expressive than (b) measures on Boolean algebras?  Results only link at (a).
% Is (c) true? Proof? [It could cover (some sort of) infinite cases...]

@@

\begin{theorem}
  Let $\mathbf{B}$ be a finite measure algebra with measure $m\colon \mathbf{B} \to
  \mathbb{R}_{\ge 0}$. Let $L \subset \mathbf{B}$ be defined as
  \[
  L = \{ l_i \mid i \in [n] \} \cup \{ \neg l_i \mid i \in [n] \}
  \]
  for some $n \in \mathbb{N}$. Finally, assume that $\mathbf{B}$ has $2^n$
  atoms, where each atom $a \in \mathbf{B}$ is an infimum
  \[
    a = \bigwedge_{i=1}^n a_i
  \]
  such that $a_i \in \{ l_i, \neg l_i \}$ for $i \in [n]$. Then there exists a
  weight function $w\colon L \to \mathbb{R}_{\ge 0}$ that makes $m$ a WMC measure if
  and only if
  \begin{equation} \label{eq:wmccondition}
  m(l \land l') = m(l)m(l')
  \end{equation}
  for all distinct $l, l' \in L$ such that $l \ne \neg l'$.
\end{theorem}

@@

  Now recall that $m = \nWMC$ and note that \cref{eq:to_prove2} can be
  multiplied by $\WMC(1)^2$ to turn the equation into one for $\WMC$ instead of
  $\nWMC$. Then
  \begin{align*}
    \WMC(k_i \land k_j) &= \sum_{\text{atoms } a \le k_i \land k_j} \WMC(a) = \sum_{\text{atoms } a \le k_i \land k_j} \prod_{m \in [n]} w(a_m) \\
                        &= \sum_{\text{atoms } a \le k_i \land k_j} w(a_i)w(a_j) \prod_{m \in [n] \setminus \{ i, j \}} w(a_m) = \sum_{\text{atoms } a \le k_i \land k_j} w(k_i)w(k_j) \prod_{m \in [n] \setminus \{ i, j \}} w(a_m) \\
    &= w(k_i)w(k_j) \sum_{\text{atoms } a \le k_i \land k_j} \prod_{m \in [n] \setminus \{ i, j \}} w(a_m) = w(k_i)w(k_j)C,
  \end{align*}
  where $C$ denotes the part of $\WMC(k_i \land k_j)$ that will be the same for
  $\WMC(\neg k_i \land k_j)$, $\WMC(k_i \land \neg k_j)$, and $\WMC(\neg k_i
  \land \neg k_j)$ as well. But then \cref{eq:to_prove2} becomes
  \[
    w(k_i)w(k_j)w(\neg k_i)w(\neg k_j)C^2 = w(k_i)w(\neg k_j)w(\neg k_i)w(k_j)C^2
  \]
  which is trivially true. By showing that WMC satisfies \cref{eq:to_prove2}, we
  also showed that it satisfies \cref{eq:to_prove}, finishing the second part of
  the proof.
\end{proof}
% TODO: the auxiliary result should be a 'claim' in-between the theorem and the
% proof.

@@

% TODO: Feedback 2: If you prove (b) above, you could motivate why weights on
% literals is attractive and whether there is a way to augment the expressivity
% of WMC while still maintaining literal level weights. Hence this action.

@@

% TODO: Feedback 2: You need to explain the significance of this result. Result
% #3: Augmented approach recovers the expressivity of (b). [This is a result,
% although not a big one.]

\section{Implications for Lifted Inference}

\subsection{Preliminaries}

\begin{definition}
  Given a BA $\mathbf{A}$, a \emph{subalgebra} is a subset $\mathbf{B} \subseteq
  \mathbf{A}$ that, together with the operations, zero, and one of $\mathbf{A}$,
  is a BA.
\end{definition}

\begin{definition}[\cite{givant2008introduction}]
  Let $\mathbf{A},$ $\mathbf{B}$, and $\mathbf{C}$ be BAs such that $\mathbf{B}$
  is a subalgebra of $\mathbf{A}$. Let $f\colon \mathbf{A} \to \mathbf{C}$ and
  $g\colon \mathbf{B} \to \mathbf{C}$ be homomorphisms. Then $f$ is an
  \emph{extension} of $g$ if $f(x) = g(x)$ for all $x \in \mathbf{B}$. If $f$ is
  an extension of each member of a family $\{ g_i \}_{i \in I}$ of
  homomorphisms, then $f$ is called a \emph{common extension} of $\{ g_i \}_{i
    \in I}$.
\end{definition}

\begin{definition}[\cite{givant2008introduction}]
  Let $\{ \mathbf{A}_i \}_{i \in I}$ be a family of subalgebras of a BA
  $\mathbf{A}$ with a family of inclusion maps $\{ \iota_i\colon \mathbf{A}_i
  \to \mathbf{A} \}_{i \in I}$. If for any BA $\mathbf{B}$ with a family of
  homomorphisms $\{ f_i\colon \mathbf{A} \to \mathbf{B} \}_{i \in I}$ there
  exists a unique common extension of $\{ f_i\colon \mathbf{A} \to \mathbf{B}
  \}_{i \in I}$ ($f\colon \mathbf{A} \to \mathbf{B}$ in the diagram),
  \[
    \begin{tikzcd}
      \mathbf{A}_i \arrow{r}{\iota_i} \arrow{rd}[swap]{f_i} & \mathbf{A} \arrow[d,dashed,"f"] \\
      & \mathbf{B}
    \end{tikzcd}
  \]
  then $\mathbf{A}$ is the \emph{internal sum}\footnote{A slightly more general
    version of this definition is also known as the free product, the Boolean
    product, and the coproduct in the category of BAs
    \cite{givant2008introduction,koppelberg1989handbook,sikorski1969boolean}.}
  of $\{\mathbf{A}_i \}_{i \in I}$. We will denote it as $\bigoplus_{i \in I}
  \mathbf{A}_i$.
\end{definition}

\begin{proposition}[\cite{sikorski1969boolean}]
  Let $\mathbf{A}$ be the internal sum of a family of BAs $\{ \mathbf{A}_i \}_{i
    \in I}$, and let $\{m_i\colon \mathbf{A}_i \to \mathbb{R}_{\ge 0} \}_{i \in
    I}$ be a family of measures. Then there exists a unique measure $m\colon
  \mathbf{A} \to \mathbb{R}_{\ge 0}$ such that, for any finite subset $J
  \subseteq I$ and family of elements $\{ x_j \in \mathbf{A}_j \}_{j \in J}$,
  \[
    m \left( \bigwedge_{j \in J} x_j \right) = \prod_{j \in J} m_j(x_j).
  \]
\end{proposition}
% TODO: this suggest a new rule for lifted inference.

\subsection{New Results}
